---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the Rmd file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

# If emo is not installed, install it.
# devtools::install_github("hadley/emo")
```

# This package heavily uses the [R Ladies meetupr package](https://github.com/rladies/meetupr)

**Authors:** [Rick Pack](http://github.com/RickPack/)

**License:** [MIT](https://opensource.org/licenses/MIT)

## Installation

To install the development version from GitHub:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("RickPack/Meetup_Excel_Animate")
```

### Global environment objects made

Note the `meetupxlanimate()` function assigns to the global environment the following objects:
* meetupxl_attendees
* meetupxl_events
* meetupxl_all_members

### Meetupr package authentication (copied from Meetupr package documentation)

As of August 15, 2019, Meetup.com switched from an API key based authentication system to [OAuth 2.0](https://www.meetup.com/meetup_api/auth/), so we now [support OAuth authentication](https://github.com/rladies/meetupr/issues/51).  The functions all have a `api_key` argument which is no longer used and will eventually be [deprecated](https://github.com/rladies/meetupr/issues/59).  In order to use this package, you can use our built-in OAuth credentials (recommended), or if you prefer, you can supply your own by setting the `meetupr.consumer_key` and `meetupr.consumer_secret` variables. 

Each time you use the package, you will be prompted to log in to your meetup.com account.  The first time you run any of the **meetupr** functions in your session, R will open a browser window, prompting you to "Log In and Grant Access" (to the **meetupr** "application").

### Function

* `meetupxlanimate()`

Making the function argument the name of the group one sees in a Meetup URL will save an animated .Gif of group membership in one's working directory and output a tibble with data about teh group.

For example, the following code will create .Gif and get data for the [Research Triangle Analysts](https://www.meetup.com/Research-Triangle-Analysts/) Meetup that gets stored in an Excel workbook Meetup_Data_Research-Triangle-Analysts.xlsx.

```{r}
library(meetupxlanimate)

urlname  <- "Research-Triangle-Analysts"
rta_data <- meetupxlanimate("Research-Triangle-Analysts")
```
