---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the Rmd file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

# If emo is not installed, install it.
# devtools::install_github("hadley/emo")
```

# This package uses edited code from R Ladies meetupr package.
At the time of package development, needed functions from the meetupr package were failing. Some function code has been modified and placed temporarily in this package in preparation for a joint June 30th, 2020 *Triangle SQL Server User Group* **(TriPASS)** / *Research Triangle Analysts* presentation(https://www.meetup.com/tripass/events/271083890/).

All responsibility for this use is Rick Pack's and the author (I) offer my apology for not planning long enough in advance to get permission for this use.

Differences between this code and the meetupr package can be viewed by comparing the repo containing the adjusted code: https://github.com/RickPack/Meetupr to https://github.com/rladies/Meetupr.

**Authors:** [Rick Pack](http://github.com/RickPack/)

**License:** [MIT](https://opensource.org/licenses/MIT)

## Installation

To install the development version from GitHub:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("RickPack/Meetup_Excel_Animate")
```

### Meetupr package authentication (copied from Meetupr package documentation)

As of August 15, 2019, Meetup.com switched from an API key based authentication system to [OAuth 2.0](https://www.meetup.com/meetup_api/auth/), so we now [support OAuth authentication](https://github.com/rladies/meetupr/issues/51).  The functions all have a `api_key` argument which is no longer used and will eventually be [deprecated](https://github.com/rladies/meetupr/issues/59).  In order to use this package, you can use our built-in OAuth credentials (recommended), or if you prefer, you can supply your own by setting the `meetupr.consumer_key` and `meetupr.consumer_secret` variables. 

Each time you use the package, you will be prompted to log in to your meetup.com account.  The first time you run any of the **meetupr** functions in your session, R will open a browser window, prompting you to "Log In and Grant Access" (to the **meetupr** "application").

### Function

* `meetupxlanimate()`

Making the function argument the name of the group one sees in a Meetup URL will save an animated .Gif of group membership in one's working directory and output a tibble with data about teh group.

For example, the following code will create .Gif and get data for the [Research Triangle Analysts](https://www.meetup.com/Research-Triangle-Analysts/) Meetup.

```{r}
library(meetupxlanimate)

urlname  <- "Research-Triangle-Analysts"
rta_data <- meetupxlanimate("Research-Triangle-Analysts")
# events <- get_events(urlname, "past")
# dplyr::arrange(events, desc(created))
```

Next we can look up all R-Ladies groups by "topic id".  You can find topic ids for associated tags by querying [here](https://secure.meetup.com/meetup_api/console/?path=/find/topics).  The `topic_id` for topic, "R-Ladies", is `1513883`.

```{r}
groups <- find_groups(topic_id = 1513883)
dplyr::arrange(groups, desc(created))
```


## How can you contribute?

Take a look at some resources:

- [https://www.meetup.com/meetup_api/](https://www.meetup.com/meetup_api/)
- [https://www.meetup.com/meetup_api/clients/](https://www.meetup.com/meetup_api/clients/)

We are looking for people to help write tests and vignettes!  You can also take a look at the open [issues](https://github.com/rladies/meetupr/issues).

--

Please note that the 'meetupr' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
